---
title: "Assignment 2"
author: "Palaniappan Perichiappan"
date: '2022-04-08'
output: 
  html_document:
  theme:
    Bootswatch: Darkly
---

#Section 1

I am going to use the dataset “Airline Safety” from the Five Thirty-Eight Github datasets. This data set contains information of safety record from various commercial airlines over the past 30 years, based on Aviation Safety Networks database. Author collected the data for 56 airlines that were in the global top 100 as of December 2012 and which have operated continuously since Jan. 1, 1985. The data contains Information such as available seat kilometers flown every week, Total number of incidents, Total number of fatal accidents and Total number of fatalities.

He defines crashes in three ways:
First, based on the rate of incidents as listed in the database, whether or not they resulted in a fatality.
Second, based on the rate of fatal accidents.
Third, by the rate of fatalities among passengers and crew on the airline.

I find that file is stored in CSV format n text format, The data is separated as ",".

#Section 2
# I used read_csv to read the data into R
```{r, include=FALSE}
library(bslib)
library(tidyverse)
library(knitr)
library(dplyr)

url <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/airline-safety/airline-safety.csv"
airlinesafety <- read.csv(url)
class(airlinesafety)
head(airlinesafety)
```



```{r, include= FALSE}
#Section 3
fil <- filter(airlinesafety, fatal_accidents_85_99>=2)
```

#section 4

This data set has `r nrow(airlinesafety)` rows and `r ncol(airlinesafety)` 

```{r, echo = FALSE}
colnames(airlinesafety)
kable(airlinesafety[1:8])
```

```{r, echo=FALSE}
text_tbl <- data.frame(
  Names = c("airline", "avail_seat_km_per_week", "incidents_85_99", "fatal_accidents_85_99", "fatalities_85_99", "incidents_00_14", "fatal_accidents_00_14", "fatalities_00_14"),
  Description = c(
    "Airline (asterisk indicates that regional subsidiaries are included)",
    "Available seat kilometers flown every week", 
    "Total number of incidents, 1985–1999",
    "Total number of fatal accidents, 1985–1999",
    "Total number of fatalities, 1985–1999",
     "Total number of incidents, 2000–2014",
    "Total number of fatal accidents, 2000–2014",
    "Total number of fatalities, 2000–2014")
)
text_tbl
```

#section 5
To check missing values i used the colsums function
```{r, echo=FALSE}
colSums(is.na(airlinesafety))
```
```{r, echo=FALSE}
kable(summary(airlinesafety), caption="The descriptive summary statistics of each column in the airline safety dataset")
```